---
title: "Evals"
author: "Sarah Supp"
date: "June 21, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

evals <- read_csv("Supp_Eval_Data.csv")
```
## Clean up eval dataframe
keep only numeric data and gather into tidy format

```{r}
#select only relevant categories, omit comments
evals2 <- evals %>%
  select(Year, Semester, Course, Section, Gender, GradYear, Major1, Major2, Reason_Taking_Course,
         Prior_Interest, Interest_Increased, Effort, Knowledge_Increased, Challenge, Overall_Rating,
         Preparedness, Clarity, Feedback, Effectiveness)

#makeit a tidy dataset
evals3 <- evals2 %>%
  gather("metric", "score", 10:19) %>%
  mutate(YearSemester = paste(Year, Semester, sep=" ")) %>%
  mutate(target = case_when(metric %in% c("Prior_Interest", "Interest_Increased", "Effort", "Knowledge_Increased", "Challenge") ~ "student",
                            metric %in% c("Preparedness", "Clarity", "Feedback", "Effectiveness") ~ "instructor",
                            metric == "Overall_Rating" ~ "course")) %>%
  mutate(majoring = case_when(Reason_Taking_Course %in% c("Major/Minor", "GE, Major/Minor") ~ "major",
                              Reason_Taking_Course %in% c("Elective", "GE", "GE, Elective", "NA") ~ "nonmajor",
                              is.na(Reason_Taking_Course) ~ "nonmajor"))

evals3$metric <- factor(evals3$metric, ordered = TRUE, levels = c("Prior_Interest", "Interest_Increased", "Effort", "Knowledge_Increased", "Challenge", "Preparedness", "Clarity", "Feedback", "Effectiveness", "Overall_Rating"))


evals_summary <- evals2 %>%
  group_by(Year, Semester, Course, Section) %>%
  summarise(student_mean = mean(c(Prior_Interest, Interest_Increased, Effort, Knowledge_Increased, Challenge), na.rm=TRUE),
            instructor_mean = mean(c(Preparedness, Clarity, Feedback, Effectiveness), na.rm=TRUE), 
            course_mean = mean(Overall_Rating)) %>%
  gather("mean", "score", 5:7) %>%
  mutate(YearSemester = paste(Year, Semester, sep=" "))

evals_summary_all_categories <- evals3 %>%
  group_by(Year, Semester, Course, Section, metric) %>%
  summarise(percent_4s_or_5s = sum(score>=4)/n()*100)
```



## Visualize Eval Results

Plot quantitative evaluation measures for students (blue), instructor (green) and the overall course rating (red).
Courses for a given semester are plotted separately, but responses from multiple sections of a course within a semester are pooled.
```{r}
ggplot(evals3, aes(metric, score)) + geom_boxplot(aes(fill=target)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_grid(YearSemester ~ Course)

```


Plot results by gender and course level

```{r}
ggplot(evals3, aes(metric, score)) + geom_boxplot(aes(fill=Gender)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + facet_wrap(~Course)

```

Plot results by Majors/nonMajors and course level. 
Generally, majors and nonmajors gave similar ratings, but where they differed non majors typically gave lower ratings.
For the intro course (DA 101), nonmajors scored lower on "interest".
For the practicum course (DA 301), nonmajors scored lower on interest, knowledge increased, challenge, and overall instructor and course rating. Nonmajors in this course are typically from math and computer science majors, so technical aspects of the course may be easier for them, while communication aspects of the course may be unexpected or underappreciated from their perspective.

```{r}
ggplot(evals3, aes(metric, score)) + geom_boxplot(aes(fill=majoring)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + facet_wrap(~Course)

```

On average, how do students feel they did, the instructor did, and the overall course rating?

```{r}

ggplot(evals_summary, aes(mean, score)) + 
  geom_point(aes(col=mean)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ylim(3,5) +
  facet_grid(Course~Year)

```

How have course evals changed through time?
*This may (or may not) be interesting once I have more course repetitions. Or, with small courses, may be fairly uninformative.
```{r}

ggplot(evals_summary, aes(YearSemester, score, group=mean)) + 
  geom_point(aes(col=mean)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  stat_smooth(method="lm", aes(col=mean, fill=mean)) + 
  ylim(1,5)

```


What percent of 4s and 5s did I get for each class? #todo: filter out NA values from calc?
```{r}
ggplot(evals_summary_all_categories, aes(metric, percent_4s_or_5s)) + 
  geom_point(aes(shape=Course, col = as.factor(Year))) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  ylim(0,100)

ggplot(evals_summary_all_categories, aes(metric, percent_4s_or_5s)) + 
  geom_bar(stat="identity") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  ylim(0,100) + facet_grid(Year~Course)
```

